---
title: "List active participants"
author: "Sage Bionetworks"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    code_fold: show
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

# Requirements

Set the value of `SYNAPSE_TOKEN` in the configuration file `.env` to one of your
Synapse personal access tokens. Token can be generated in Synapse via your User
Menu > Settings > Persona Access Tokens.

# Conda environments

List the Conda environments.

```{r}
library(reticulate)
options(reticulate.repl.quiet = TRUE)
conda_list(conda = "auto")
```

Activate the environment `challenge-analysis`.

```{r}
use_condaenv("challenge-analysis", required = TRUE)
```

## Input

```{r}
evaluationId <- '9614453'
```

## Data

Get information about the evaluation queue:

```{r}
evaluation <- syn$getEvaluation(evaluationId)
evaluation$name
```

Get the Synapse user ID of contributors associated to a successful submission:

```{python}
contributor_ids = set()
status_set = set()

# TODO avoid loops/nested loops
for submission in r.syn.getSubmissions(r.evaluation):
  status = r.syn.getSubmissionStatus(submission)
  if status.status == 'ACCEPTED':  # usually SCORED
    for contributor in submission.contributors:
      contributor_ids.add(contributor['principalId'])
```

Get the Synapse profile of the contributors:

```{python}
profiles = []

for contributor_id in contributor_ids:
  profiles.append(r.syn.getUserProfile(contributor_id))
```

Get the first name, last name and @synapse.org email address of the
contributors:

```{r}
contacts <- do.call(rbind, lapply(py$profiles, function(profile) {
  data.frame(
    firstName = tryCatch(profile$firstName, error=function(err) NA),
    lastName = tryCatch(profile$lastName, error=function(err) NA),
    email = tryCatch(paste0(profile$userName, '@synapse.org'), error=function(err) NA)
  )
}))
contacts
```
